Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-09-27 paper/paper.tex
Works on sat too

These beliefs are not entirely unfounded: none of the matching algorithms considered in these papers
will immediately detect if a pattern contains two red vertices, whilst the target graph contains
only one. This kind of flaw \emph{should} be picked up at the top of search by an all-different
propagator \citep{DBLP:conf/aaai/Regin94}.  However, as \citet{DBLP:journals/pvldb/KatsarouNT15}
note, some variation on VF2 \citep{Cordella:2004} is the usual matching algorithm of choice for
graph database systems, although \citeS{DBLP:journals/jacm/Ullmann76}'s algorithm is sometimes
chosen. (Other approaches have been considered: for example, \citet{DBLP:journals/pvldb/ShangZLY08}
propose an algorithm which makes use of the frequency of various features to guide search.
\citet{DBLP:journals/pvldb/LeeHKL12} determine experimentally that this technique tends to be very
effective, even on families of graphs for which it was not designed.) We believe it would be
unlikely to cause too much astonishment if we suggested that a better matching algorithm could be
dropped in as a black box replacement in graph databases systems to improve their performance.
However, it appears not to have occurred to the graph databases community that a better subgraph
isomorphism algorithm could invalidate the premise underlying the entire filter / verify approach.
Eliminating this filtering step would not merely be a matter of simplicity: indices take ??  hours
to build.

>>>>

These beliefs are not entirely unfounded: none of the matching algorithms considered in these papers
will immediately detect if a pattern contains two red vertices, whilst the target graph contains
only one. This kind of flaw \emph{should} be picked up at the top of search by an all-different
propagator \citep{DBLP:conf/aaai/Regin94}.  However, as \citet{DBLP:journals/pvldb/KatsarouNT15}
note, some variation on VF2 \citep{Cordella:2004} is the usual matching algorithm of choice for
graph database systems, although \citeS{DBLP:journals/jacm/Ullmann76}'s algorithm is sometimes
chosen. Other approaches have been considered: for example, \citet{DBLP:journals/pvldb/ShangZLY08}
propose an algorithm which makes use of the frequency of various features to guide search.
\citet{DBLP:journals/pvldb/LeeHKL12} determine experimentally that this technique tends to be very
effective, even on families of graphs for which it was not designed.) We believe it would be
unlikely to cause too much astonishment if we suggested that a better matching algorithm could be
dropped in as a black box replacement in graph databases systems to improve their performance.
However, it appears not to have occurred to the graph databases community that a better subgraph
isomorphism algorithm could invalidate the premise underlying the entire filter / verify approach.

?? Eliminating this filtering step would not merely be a matter of simplicity: indices take ??  hours
to build.

?? Additionally, this stuff works on satisfiable instances too.
